\LARGE \bf Enriching Robot's Actions with Affective Movements

### 2017-03-19 RO-MAN-2017-2/Parts/SimpleActions.tex
Update SimpleActions.tex

In order to generate a system that could be used in diverse platforms require an abstraction level in which all of them could fall. Therefore simple and compound actions are used to achieve this goal. Simple actions are actions that are considered as primitives: they are used as building blocks. Therefore, these actions are described in the system and are the ones in which the emotional enrichment takes place. Their description specifies mandatory and optional parameters that are required to execute an action. Compound actions are actions that are created from simple actions. These actions are not implemented in the system, but, if it is needed, they can be described in it (e.g. compound actions that are used often).

@@

%TODO add an example for this, very simple and presenting how to do it

>>>>

In order to generate a system that could be used in diverse platforms, an abstraction level in which all of them could fall is required. Therefore simple and compound actions are used to achieve this goal. Simple actions are actions that are considered as primitives: they are used as building blocks. Therefore, these actions are described in the system and are the ones in which the emotional enrichment takes place. Their description specifies mandatory and optional parameters that are required to execute an action. Compound actions are actions that are created from simple actions. These actions are not implemented in the system, but, if it is needed, they can be described in it (e.g., compound actions that are used often).

@@

%TODO add an example for this, very simple and presenting how to do it. IT WOULD BE VERY NICE
